Modalities for Virtualizing Memory Addresses

### 2022-12-04 intro.tex
+

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor. Up until now, program logics ~\cite{} has already approached some verification challenges manifesting itself in this (or similar) forms ~\cite{}. One of the most recent ones introduces reasoning principles for heap management under garbage collection ~\cite{}. In this work, a set of \textit{already iterated} memory locations (\texit{roots}) identified based on their \textit{stackability}, i.e. a metric determines a memory location is safe to allocate/reclaim or not, more specifically implemented as an abstraction holding mappings from memory locations to factions where a complete fraction (1) asserts the fact that the relevant memory location is safe for allocation. This work, in fact, distinguishes itself as \textit{"High Level"} from its predecessor fundamentally by its new logical constructions that remove the burden of keeping explicit roots of each memory location, and it is achieved through ~\cite{}
\begin{itemize}
\item a custom-tailored weakest-precondition modality defined to operate with \textit{Stackable} assertion.
\item a set of logical rules defined over this modality allows us
  \begin{itemize}
  \item  a light-weight reasoning by the replacement of explicit root tracking ~\cite{} with a set of \textit{stackable} bookkeeps already \textit{iterated} (logically \textit{framed-out} in the pre/post condition). 
  \item  an intuitive reasoning over the data structure (a set of roots), e.g. \textit{allocation} as introduction (expansion of \textit{Stackable} set), and binding of a variable to a value as \textit{elimination} of individual \textit{stackable} assertion for a single memory location into its modal weakest-precondition
  \end{itemize}
\end{itemize}
Despite its modal flavor, and the abstraction of \texit{already iterated stackable memory locations} set enabling a good summarization of resources to be framed out, we think that it is worth raising attention on the methodology followed for bringing the logic Madiot et.al ~\cite{} the the \textit{higher-level} version from Moine et.al. ~\cite{} around
\begin{itemize}
\item {more light-weight} such that
  \begin{itemize}
  \item modal abstractions remove the burden of carrying the resource that ---
  \item >>>contingency as a modal abstractions
  \item 
  \item we do no
  \end{itemize}
\item {more intuitive} modal abstraction definition, together with relations defined
\begin{itemized}
  \end{itemize}
\end{itemize}

>>>>

This kind of context-dependent assertion, where a fact may be true in one address space but not others, has a modal flavor. Up until now, program logics ~\cite{} has already approached some verification challenges manifesting itself in this (or similar) forms ~\cite{}. One of the most recent ones introduces reasoning principles for heap management under garbage collection ~\cite{}. In this work, a set of \textit{already iterated} memory locations (\textit{roots}) identified based on their \textit{stackability}, i.e. a metric determines a memory location is safe to allocate/reclaim or not, more specifically implemented as an abstraction holding mappings from memory locations to factions where a complete fraction (1) asserts the fact that the relevant memory location is safe for allocation. This work, in fact, distinguishes itself as \textit{"High Level"} from its predecessor fundamentally by its new logical constructions that remove the burden of keeping explicit roots of each memory location, and it is achieved through ~\cite{}
\begin{itemize}
\item a custom-tailored weakest-precondition modality defined to operate with \textit{Stackable} assertion.
\item a set of logical rules defined over this modality allows us
  \begin{itemize}
  \item  a light-weight reasoning by the replacement of explicit root tracking ~\cite{} with a set of \textit{stackable} bookkeeps already \textit{iterated} (logically \textit{framed-out} in the pre/post condition). 
  \item  an intuitive reasoning over the data structure (a set of roots), e.g. \textit{allocation} as introduction (expansion of \textit{Stackable} set), and binding of a variable to a value as \textit{elimination} of individual \textit{stackable} assertion for a single memory location into its modal weakest-precondition
  \end{itemize}
\end{itemize}
Despite its modal flavor, and the abstraction of \textit{already iterated stackable memory locations} set enabling a good summarization of resources to be framed out, we think that it is worth raising attention on the methodology followed for bringing the logic Madiot et.al ~\cite{} the the \textit{higher-level} version from Moine et.al. ~\cite{} around the following issues.
\begin{remark}[Hiding What is Stackable in a Modal Context?] 
\end{remark}
\begin{remark}[Custom-Tailored Modal Abstractions for a Each Stackable Data-Structure]
\end{remark}
\begin{remark}[Not only Being Stackable But How?]
\end{remark}
